RDF Validation Requirements - Evaluation and Logical Underpinning

### 2015-01-13 paper/RDF validation requirements/RDF validation requirements.tex
minor
small touch.
authors
abstract

%
%
\title{RDF Validation Requirements - Evaluation and Logical Underpinning}
\subtitle{}
%
\titlerunning{XXXXX}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Thomas Bosch\inst{1} \and Andreas Nolle\inst{2} \and Erman Acar\inst{3}}
%
\authorrunning{XXXXX} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\institute{GESIS – Leibniz Institute for the Social Sciences, Germany\\
\email{thomas.bosch@gesis.org},\\ 
\and
Albstadt-Sigmaringen University, Germany \\
\email{nolle@hs-albsig.de}
\and
University of Mannheim, Germany \\
\email{\{christian,erman,kai\}@informatik.uni-mannheim.de} 
}

@@

\begin{abstract}
There are many case studies for which the formulation of RDF constraints and the validation of RDF data conforming to these constraint is very important.  
The W3C and the DCMI working groups on RDF validation identified many RDF validation requirements,
whereupon we initiate an RDF validation requirements database which is available to contribute at \url{http://purl.org/net/rdf-validation}.
The intention of this database is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation.
Although, there are multiple constraint languages which can be used to formulate RDF constraints (associated with these requirements), 
there is no standard way to formulate RDF constraints.

This paper serves to evaluate to which extend each requirement is satisfied by each of these constraining languages.
We take reasoning into account as a pre-validation step and distinguish between OWL 2 QL and OWL 2 DL constructs to express particular constraints.
We classify constraints according to a developed classification mechanism for constraints.
We show that each constraint can be mapped to an ontology describing RDF constraints generically.
If a constraint can be expressed in DL, we add the mapping to DL and to the generic constraint in order to logically underpin associated requirements.
If a constraint cannot be expressed in DL, we only add the mapping to the generic constraint.

>>>>

%
%
\title{RDF Validation Requirements - Evaluation and Logical Underpinning}
\subtitle{}
%
\titlerunning{XXXXX}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Thomas Bosch\inst{1} \and Andreas Nolle\inst{2} \and Erman Acar\inst{3} \and Kai Eckert \inst{3}}
%
\authorrunning{XXXXX} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\institute{GESIS – Leibniz Institute for the Social Sciences, Germany\\
\email{thomas.bosch@gesis.org},\\ 
\and
Albstadt-Sigmaringen University, Germany \\
\email{nolle@hs-albsig.de}
\and
University of Mannheim, Germany \\
\email{\{erman, kai\}@informatik.uni-mannheim.de}}

@@

\begin{abstract}
There are many case studies for which the formulation of RDF constraints and the validation of RDF data conforming to these constraint is very important.  
The W3C and the DCMI working groups on RDF validation identified many RDF validation requirements,
whereupon we initiate an RDF validation requirements database which is available to contribute at \url{http://purl.org/net/rdf-validation}.
The intention of this database is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation.
Although, there are multiple constraint languages which can be used to formulate RDF constraints (associated with these requirements), 
there is no standard way to formulate them.
This paper serves to evaluate to which extend each requirement is satisfied by each of these constraint languages.
We take reasoning into account as an important pre-validation step and map constraints to DL
%, and distinguish between OWL 2 QL and OWL 2 DL constructs to express particular constraints.
%We classify constraints according to a developed classification mechanism for constraints.
in order to show that each constraint can be mapped to an ontology describing RDF constraints generically.
%If a constraint can be expressed in DL, we add the mapping to DL and to the generic constraint in order to logically underpin associated requirements.
%If a constraint cannot be expressed in DL, we only add the mapping to the generic constraint.
